Data Preparation

### 2019-01-14 Data Preparation.Rmd
clean code

```{r import d_course d_assessment and d_ILO, cache = TRUE}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
print(d_course)
d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
  mutate(assessment_covered = as.logical(assessment_covered)) %>%
  filter(assessment_covered) %>%
  select(- assessment_covered) %>%
  arrange(Code)
print(d_assessment)
d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
  mutate(AoD_covered = as.logical(AoD_covered)) %>%
  rename(ILO = Objectives) %>%
  filter(AoD_covered) %>%
  select(- AoD_covered) %>%
  arrange(Code)
print(d_ILO)
```

@@

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv("Raw Grades/grades1.csv", 
           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(),`End Date` = col_character()
                              )
           ),
  read_csv("Raw Grades/grades2.csv", 
           col_types = cols(`Program (Abbreviation)`=col_character(), `Appraisal Status`= col_character(), `Module Booking Reason (Description)`= col_character(), `Object name` = col_character(), `Start date` = col_character(), `End Date` = col_character()
           )
           )
  )
```

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_ILO)
```

@@

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  select(Code, AoD) %>%
  distinct
print(d_AoD_assessment)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)
d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))
d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))
d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code")
rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
print(d_course_detail)
```

```{r join d_course_detail}
d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
rm(d_course_detail)
print(d_course)
```

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```

##Textual Data

@@

####Course Catalogues
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

@@

#### Course Manuals
#####Extracting Full Text
(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))

>>>>

```{r import d_course d_assessment and d_ILO, cache = TRUE}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848')
print(d_course)

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
  mutate(assessment_covered = as.logical(assessment_covered)) %>%
  filter(assessment_covered) %>%
  select(- assessment_covered) %>%
  arrange(Code)
print(d_assessment)

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
  mutate(AoD_covered = as.logical(AoD_covered)) %>%
  rename(ILO = Objectives) %>%
  filter(AoD_covered) %>%
  select(- AoD_covered) %>%
  arrange(Code)
print(d_ILO)
```

@@

```{r import d_transcript, cache = TRUE}
d_transcript <- rbind(
  read_csv(
    "Raw Grades/grades1.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(),
      `Module Booking Reason (Description)` = col_character(),
      `Object name` = col_character(),
      `Start date` = col_character(),
      `End Date` = col_character()
      )
    ),
  read_csv(
    "Raw Grades/grades2.csv",
    col_types = cols(
      `Program (Abbreviation)` = col_character(),
      `Appraisal Status` = col_character(), 
      `Module Booking Reason (Description)` = col_character(), 
      `Object name` = col_character(), 
      `Start date` = col_character(), 
      `End Date` = col_character()
      )
    )
  )
```

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  distinct(Code, AoD)
print(d_AoD_ILO)
```

@@

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  distinct(Code, AoD)
print(d_AoD_assessment)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  distinct(Code, ILO) %>%
  count(Code) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code")

rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
print(d_course_detail)
```

```{r join d_course_detail}
d_course <- d_course %>%
  full_join(d_course_detail, by = "Code") %>%
  select(Code, `Course Title`, Cluster,
         n_ILO,
         n_assessment, `Assessments Covered`,
         n_AoD, `AoD Covered`, 
         everything())

rm(d_course_detail)
print(d_course)
```

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))

print(select(d_course, Code, Letters, Number, Level))
```

@@

#### Extractin Text: Course Catalogues
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

@@

#### Extracting Text: Course Manuals
(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))
